---
title: "Using ldrd2020050"
output:
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 3
vignette: >
  %\VignetteIndexEntry{Using ldrd2020050}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ldrd2020050)
library(ggplot2)
```

# Reading data

We generally store project data as dataframes, in the RDS format. Read such
a file using `readRDS`.

In this vignette, we will rely upon a dataset that is part of the package:

```{r}
data(rawcornerpeak)
head(rawcornerpeak)
```

This is what we call a *raw* integration dataframe.

# Transform *raw* dataframe to our canonical tibble format

Use `augment_raw_dataframe` to create an *augmented* integration dataframe.
The augmented dataframe (actually a tibble) has some additional columns:
a *length* for each
dimension (`len_i` for dimension `i`),
and a *volume* (`vol`).
The `active` column from the raw dataframe is transformed from `integer` to `logical`.
The names of the dimensions are also canonicalized, to the form `dim_i_lo` and `dim_i_hi`.

```{r}
cornerpeak <- augment_raw_dataframe(rawcornerpeak)
cornerpeak
```

# Summarizing by iteration

Most of our analysis is done on an *iteration summary* dataframe (actually a tibble).
This dataframe contains one row per iteration.
The column names that start with *act* summarize regions that are *active*,
which means they are due to be split in the next iteration
(if there is a next iteration).
Column names that start with *fin* summarize regions that are *finished*,
which means they will not be split,
and also will not be present in the next iteration.
Column names beginning with *it* are the combination of the *act* and *fin* columns;
they represent that totals *just for the current iteration*.
Column names beginning with *tot* represent the total values
up to and including the current iteration.
These are the values the integration routine would return,
if it stopped at the given iteration.

```{r}
iter <- make_iteration_dataframe(cornerpeak)
iter
```

# Sanity check plots

Most important is that the integral estimate converges to a correct answer:

```{r}
ggplot(iter, aes(iteration, tot.est, ymin=tot.est-tot.err, ymax=tot.est+tot.err)) +
  geom_errorbar(width = 0.2) +
  geom_point() +
  labs(x="iteration", y="Integral estimate")
```

